---
title: "arctic topics"
output:
  
  html_document: default
  pdf_document: default
always_allow_html: yes
---

##Topic Scores
This analysis analyzes Arctic Council speeches and national arctic strategy documents by comparing the relative frequencies of words belonging to ten different topics. We have defined these topics by creating dictionaries of commonly mentioned words that relate to each.

The method used here calculates the fraction of words in each document belonging to each topic to calculate a document-level score. It then averages document-level scores for each country to create a country-level score.

###Preparing the data

This section loads the libraries and the text files from four different folders.

This version does not remove stop words, punctuation, etc. This should not adversely affect our results, since we are using a dictionaries method to calculate our scores.


```{r, message=FALSE, warning=FALSE}

library(igraph)
library(tidyverse)
library(tidytext)
library(readtext)
library(quanteda)
library(dplyr)
library(stringr)
library(plotly)
library(rworldmap)
library(ngram)

#This sets the directory where the texts are located
DATA_DIR <- "C:/Users/laura/OneDrive/Desktop/Krogh-Arctic/Strategy Documents (new)"  

#This command reads in all the file names and stores the texts in a tidy dataframe
strategy <- readtext(paste0(DATA_DIR, "/*"))

#This identifies the row names of the dataframe
row.names(strategy) <- strategy$doc_id

#Do again for the second folder
DATA_DIR <- "C:/Users/laura/OneDrive/Desktop/Krogh-Arctic/Observer Documents"  
observer <- readtext(paste0(DATA_DIR, "/*"))
row.names(observer) <- observer$doc_id

#Third folder
DATA_DIR <- "C:/Users/laura/OneDrive/Desktop/Krogh-Arctic/Arctic Speeches"  
speeches <- readtext(paste0(DATA_DIR, "/*"))
row.names(speeches) <- speeches$doc_id

#Fourth folder
DATA_DIR <- "C:/Users/laura/OneDrive/Desktop/Krogh-Arctic/Official Speeches and Documents"  
officialspeeches <- readtext(paste0(DATA_DIR, "/*"))
row.names(officialspeeches) <- officialspeeches$doc_id


```

###Combining the data frames and restructing

```{r}
#unnest the tokens (words) and create a new data frame with each word as one row
strategydf <- unnest_tokens(strategy, word, text)

observerdf <- unnest_tokens(observer, word, text)

speechesdf <- unnest_tokens(speeches, word, text)

officialspeechesdf <- unnest_tokens(officialspeeches, word, text)

#combine full text (nested) versions into a single df
fulltexts <- strategy %>%
  full_join(observer) %>%
  full_join(speeches) %>%
  full_join(officialspeeches) 

#combine the three unnested versions into a single df
totaldf <- strategydf %>%
  full_join(observerdf) %>%
  full_join(speechesdf) %>%
  full_join(officialspeechesdf) 

#calculate the document lengths by counting how many words are in each
words <- totaldf %>%
  group_by(doc_id) %>%
  mutate(length=n()) %>%
  ungroup()

#separate the doc_id loaded from the filename into country and everything that follows
words <- words %>%
  mutate(doc_id2=doc_id) %>%
  separate(doc_id2, c("country", "misc"), sep = "_") 

#the same for the full text version
fulltexts <- fulltexts %>%
  mutate(doc_id2=doc_id) %>%
  separate(doc_id2, c("country", "misc"), sep = "_") 

```

###Defining the topic dictionaries
There are ten topics:
1. environment
2. indigenous
3. transport
4. development
5. tourism
6. resources
7. fisheries
8. diplomacy
9. security
10. legal

```{r}

#Environment
#define all the words in each dictionary
environment <- data.frame(c("research", "science", "scienti", "environment","climate","climate change","ocean","sea","sea level","atmosphere", "air", "ice","warm", "melt","knowledge", "station","glaciological","geological","biological","ecosystem","paleoclimate","laboratory","conservation","preservation","temperature","data","measurement","study","precipitation","pollution","cryospheric","publication","biodiversity","academic", "glacier", "disaster", "observe", "trend","predict","species","force","global warming","protect" ))

#name the column for future reference
colnames(environment) <- "topic"

#add a new column identifying these words as relating to the environment topic, for future reference
environment <- mutate(environment, name = "environment")


#Indigenous
indigenous <- data.frame(c("nation", "local", "indigenous", "peoples", "community", "human", "social", "lives", "condition", "inhabitants", "well-being", "language", "health", "traditional", "culture", "rural", "residents"))
colnames(indigenous) <- "topic"
indigenous <- mutate(indigenous, name = "indigenous")


#Transport
transport <- data.frame(c("transportation", "shipping", "import", "export", "maritime", "transport", "ship", "vessel", "navigation", "route", "channel", "northeast passage", "northwest passage", "northern sea route", "voyage", "commercial", "trade", "icebreakers", "water", "transit"))
colnames(transport) <- "topic"
transport <- mutate(transport, name = "transport")


#Development
development <- data.frame(c("Sustainable","development","economic","globalization","economic zones","commercial","production","strategy","benefit","capital","market","enterprise","opportunity","business","infrastructure","fund","industry"))
colnames(development) <- "topic"
development <- mutate(development, name = "development")


#Tourism
tourism <- data.frame(c("tourism","tourists","rescue","ecotourism"))
colnames(tourism) <- "topic"
tourism <- mutate(tourism, name = "tourism")


#Resources
resources <- data.frame(c("oil","industr","resource","technology","energy","gas","carbon","infrastructure","build","exploit","mine","utilization","exploitation","natural","mineral","geothermal","wind","exploration","consumer","pipeline","extraction", "seabed", "metal", "metals", "seafloor", "offshore"))
colnames(resources) <- "topic"
resources <- mutate(resources, name = "resources")


#Fisheries
fisheries <- data.frame(c("fish","fisheries","fishing","aquaculture","goods"))
colnames(fisheries) <- "topic"
fisheries <- mutate(fisheries, name = "fisheries")


#Diplomacy
diplomacy <- data.frame(c("strengthen","joint","relationship","peace","integration","cooperation","international","relations","diplomatic","contribute","parties","stability","equality","participants","connect","multilateral","bilateral","regional","global","coalition","collaboration","coordination","share","same","affairs","harmony","alliance","partnership","freedom","political","meet"))
colnames(diplomacy) <- "topic"
diplomacy <- mutate(diplomacy, name = "diplomacy")


#Security
security <- data.frame(c("sovereignty", "state", "nation", "secure", "security", "stakeholder", "governance", "claim", "interests", "territory", "zone", "own", "influence", "military", "defend", "defense", "position", "independent"))
colnames(security) <- "topic"
security <- mutate(security, name = "security")

#Legal
legal <- data.frame(c("continental shelf", "rule", "UNCLOS", "jurisdiction", "rights", "spitsbergen", "legal", "law", "just", "treaty", "treaties", "regulation", "boundary", "boundaries", "delimitation", "EEZ", "arbitration", "court", "ICJ", "ruling", "protocol", "reservation", "convention", "contiguous zone", "right", "ratification", "ratified"))
colnames(legal) <- "topic"
legal <- mutate(legal, name = "legal")
```

###Generating scores
Document scores are generated by counting the frequency of words relating to each topic in each document. Country scores are generated by averaging all the document scores for a single country. They are them standardized by subtracting the average country-topic score and dividing by the standard deviation. 

These scores are then broken into categories:
High = top 40%
Medium = next 20%
Low = next 20%
Very low = next 20%

```{r}

#define a function that will generate country scores for the provided topic

countwords2 <- function(topic){

#each row contains the full text of a single document  
docscores <- fulltexts

#add a new column with the total number of times words from that topic appeared in the full text
#loop through each word in the topic, count how many times it appears, and add them for all words in the topic
docscores$count <- sapply(fulltexts$text, function(x) sum(apply(topic, 1, function(z) str_count(x, z)))) 

#add a new column with the document length
docscores$doclength <- sapply(fulltexts$text, function(x) wordcount(x))

#add a new column with score, which equals the frequency divided by the total length
docscores <- docscores %>%
  mutate(score=count/doclength) 

#calculate country scores by averaging document scores
countryscores <- docscores %>%
  group_by(country) %>%
  summarize(country_score = mean(score)) %>%
  mutate(name =topic$name[1] )
}

#Environment
#calculate scores
environment_scores2 <- countwords2(environment)

#Indigenous
indigenous_scores2 <- countwords2(indigenous)

#Transport
transport_scores2 <- countwords2(transport)

#Development
development_scores2 <- countwords2(development)

#Tourism
tourism_scores2 <- countwords2(tourism)

#Resources
resources_scores2 <- countwords2(resources)

#Fisheries
fisheries_scores2 <- countwords2(fisheries)

#Diplomacy
diplomacy_scores2 <- countwords2(diplomacy)

#Security
security_scores2 <- countwords2(security)

#Legal
legal_scores2 <- countwords2(legal)

#combine all the scores together
country2df <- environment_scores2 %>%
   full_join(indigenous_scores2) %>%
    full_join(transport_scores2)  %>%
    full_join(development_scores2) %>%
  full_join(tourism_scores2) %>%
  full_join(resources_scores2) %>%
 full_join(fisheries_scores2) %>%
 full_join(diplomacy_scores2) %>%
 full_join(security_scores2) %>%
  full_join(legal_scores2)


```

##Creating the categories

```{r}

scoremean <- mean(country2df$country_score)
scoresd <- sd(country2df$country_score)

country2df <- country2df %>%
  mutate(sdmean = (country_score-scoremean)/scoresd)

scores3q <- quantile(country2df$sdmean, probs = c(0, 0.20, 0.40, 0.60, 1))

country3df <- country2df  %>%
  mutate(rank = ifelse(sdmean < scores3q[2], "very low", 
                       ifelse(sdmean>scores3q[2] & sdmean < scores3q[3], "low", 
                               ifelse(sdmean>scores3q[3] & sdmean < scores3q[4], "medium", "high"))))
  
cleantable3 <- country3df %>% spread(name, rank) %>%
  select(country, development:transport)  %>%
  group_by(country) %>%
 arrange(country, environment, diplomacy, legal, indigenous, development, transport, fisheries, resources, security)

 cleantable3

 write.csv(cleantable3, file="cleantable3.csv")

```


##More Graphs

```{r}
membersdf <- country3df 

membersdf$member <- ifelse(membersdf$country=="Canada"|membersdf$country=="Denmark" | membersdf$country=="Greenland" | membersdf$country=="Finland" | membersdf$country == "Iceland" | membersdf$country=="Norway" | membersdf$country == "Russia" | membersdf$country == "Sweden" | membersdf$country=="US", "member", "nonmember")

multi.indigenous <- ggplot(filter(membersdf, name=="indigenous"), aes(x=reorder(country,country_score), y=country_score, color=member)) + geom_point() + coord_flip() +
  ggtitle("Indigenous") + theme(axis.title.y = element_blank())
ggplotly(multi.indigenous)

countrymutli <- country2df %>%
filter(country=="US"|country=="Russia"|country=="China") %>%
  filter(name!="tourism" & name!= "environment" & name != "fisheries")

p.countrymulti <- ggplot(countrymutli, aes(x=name, y=country_score, fill=country)) + geom_bar(stat="identity", position="dodge") + theme(axis.text.x = element_text(angle = 90, hjust = 1), axis.title.x = element_blank())
ggplotly(p.countrymulti)

```

